Event History Analyses for psychological time-to-event data: A tutorial in R with examples in Bayesian and frequentist workflows

### 2024-10-21 manuscript/manuscript.Rmd
correct small error

Based on Figure 6 and Table 4, we see that at the beginning of the experiment (trial 500), congruent and incongruent primes have a positive effect in time bin (200,240] on cloglog-hazard, relative to the cloglog-estimate in the baseline condition (no prime; red striped lines in Figure 6). For example, the hazard ratio shows that the hazard of response occurrence for congruent primes is estimated to be 8.82 times higher than that for no-prime trials, in bin (200,240] of trial 500. Incongruent primes also have a negative effect on cloglog-hazard in bins (320,360], (360,400], and (400,440]. For example, in bin (320,360], the hazard ratio shows that the hazard of response occurrence for incongruent prime is estimated to be .34 times smaller than that for no-prime trials. While the early positive effects reflect responses to the prime stimulus, the later negative effect for incongruent primes likely reflects response competition between the prime-triggered response (e.g., left) and target-triggered response (e.g., right)

>>>>

Based on Figure 6 and Table 4, we see that at the beginning of the experiment (trial 500), congruent and incongruent primes have a positive effect in time bin (200,240] on cloglog-hazard, relative to the cloglog-hzard estimate in the baseline condition (no prime; red striped lines in Figure 6). For example, the hazard ratio shows that the hazard of response occurrence for congruent primes is estimated to be 8.82 times higher than that for no-prime trials, in bin (200,240] of trial 500. Incongruent primes also have a negative effect on cloglog-hazard in bins (320,360], (360,400], and (400,440]. For example, in bin (320,360], the hazard ratio shows that the hazard of response occurrence for incongruent prime is estimated to be .34 times smaller than that for no-prime trials. While the early positive effects reflect responses to the prime stimulus, the later negative effect for incongruent primes likely reflects response competition between the prime-triggered response (e.g., left) and target-triggered response (e.g., right)
